Stack Safety is a Security Property

### 2021-04-17 tex/main.tex
comments and polishing on 6 and 8

\vspace*{-1ex}
\judgmentthree[ReturnRec]
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
              {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
              {\(\domMap'' = \domMap'[\components \mapsto \unsealed]\)}
              {\(\mach,(\domMap,\underscore::\rts) \stepsto_C \domMap'',\rts'\)}

\vspace*{-3.5ex}
\judgment[ Default]
         {}
         {\(\underscore,\context \stepsto_C \context\)}

@@

\definition
Let the protected set of a context, \(\prot(\domMap,\rts)\), be the
set of components \(\component\) such that \(\domMap ~ \component = \sealed{\depth}\)
for some depth \(\depth\).

\definition
A system enjoys \textit{\textbf{stepwise stack integrity}} if, for any reachable state
\(\mpcstatename\) such that \(\mpcstatename \stepstocon \mpcstatename'\),
and any component \(\component \in \prot(\domMap,\rts)\),
\(\pi_\mach(\mpcstatename') ~ \component = \pi_\mach(\mpcstatename) ~ \component\).
\apt{but now $dm$ and $rts$ are unbound}.

@@

\definition \(\MPCT^*\) is the \emph{call set}, defined as
\[\begin{aligned}
\bigcup_{\depth \in \mathbb{Z}} \{\MPCT, \neg f_\depth | \MPCT\langle f_\depth \rangle
\text{ is a reachable segment}\} \hspace{1em} &
\text{where } f_\depth ~ (\mach,\pol,(\domMap,\rts)) \triangleq |\rts| \geq \depth \\
\end{aligned}\]

We term \(\neg f_\depth\) the {\em break condition} \(\brk\), a predicate on
states that holds on \(\MPCT\)'s final state, {\em unless it terminated prematurely due to a failstop}.

@@

\begin{minipage}{.3\textwidth}
\judgment{}
         {\(\mpcstatename \doteq \npcstatename\)}
\end{minipage}
\begin{minipage}{.6\textwidth}
\judgmenttwo{\(\mach, \pi_\mach(\head(\machT)) \diamond \nach, \pi_\mach(\head(\nachT))\)}
            {\(\machT \doteq \nachT\)}
            {\(\notfinished{(\mach,\underscore,\underscore)}{\machT} \doteq \notfinished{(\nach,\underscore,\underscore)}{\nachT}\)}
\end{minipage}

\definition
Let the secret set of a context, \(\secret(\domMap,\rts)\), be the
set of components \(\component\) such that \(\domMap ~ \component \not = \outside\).

\definition
For any \(\MPCT,\brk \in \MPCT^*\) with \(\head(\MPCT) = \mach,\pol,\context\),
let \(\components = \mathit{secret}(\context)\).
A system enjoys \textbf{\textit{stepwise stack confidentiality}} if,
for any \(\nach\) such that \(\mach \approx_\components \nach\) and the induced trace
\(\NPCT\) such that \(\nach,\pol,\domMap \hookrightarrow \NPCT | \brk\),
\(\MPCT \doteq \NPCT\) holds.\apt{I'm worried about quantifier order here. Surely $n$ needs to be
  universally quantified, and probably also \(\MPCT\) (?) }
\sna{Better?}

@@

In other words, stepwise stack confidentiality states that if we vary every component of the stack,
the resulting trace (starting in the same policy state) steps in lockstep with the
original trace until both have reached the break condition.
%
Note that \(\MPCT\) may contain nested calls; these must also respect the secrecy
of the components in \(\components\), and in addition their subtraces are also in
\(\MPCT^*\), and therefore confidentiality must hold on them separately. \(\NPCT\)
will contain these calls and returns as well, so its return stack pushes and pops
in lockstep until it breaks at the final return.

Finally, we formalize a version of WBCF, which capture the same informal idea
as that of \citet{Skorstengaard+19b} using our notion of contexts.
\definition
A system enjoys \textit{\textbf{well-bracketed control flow}} when, for every pair of reachable states
\(\mpcstatename = (\underscore,\underscore,(\underscore,\rts))\) and
\(\mpcstatename' = (\underscore,\underscore,(\underscore,\rts'))\) such that
\(\mpcstatename \stepsto \mpcstatename'\), if \(|\rts'| < |\rts|\), then
\(|\rts'| = |\rts|-1\)

@@

%\definition A system enjoys {\em well-bracketed control flow} if for all
%reachable states \(\mpcstatename\) and \(\mpcstatename'\) such that
%\(\mpcstatename \stepstocon \mpcstatename'\), if
%\(\pi_c(\mpcstatename) = (\underscore, \underscore::\rts)\) and \(\pi_m(\mpcstatename)\)
%is annotated as a return, then \(\pi_c(\mpcstatename) = (\underscore, \rts)\).

@@

%\definition A system enjoys {\em well-structured control flow} if for all
%reachable states \(\mpcstatename\) and \(\mpcstatename'\) such that
%\(\mpcstatename \stepstocon \mpcstatename'\), if
%\(\pi_c(\mpcstatename) = (\underscore,\underscore,\underscore,\stackid)\) and \(\pi_m(\mpcstatename)\)
%is annotated as a return, then \(\pi_c(\mpcstatename) = (\underscore,\underscore,\underscore,\stackid')\)
%where \(\stackid \not = \stackid'\).

@@

Naturally, testing also revealed a number of errors in our
implementation of the enforcement mechanism (the original was written in C++
and targeted ARM machine code
%\bcp{right?}\leo{yeah}
; we re-implemented it in Coq targeting RISC-V).  These errors ranged
from trivial typos to ones that required an intriguingly complex setup
to appear.  The most interesting bug (included in the table as row
{\em HEADER\_NO\_INIT}) was that, on our first try, the blessed call
sequence %/policy combination\apt{??}
did not initialize all locations for the
newly allocated stack frame correctly, but left some of them as
$\tagNoDepth$. This allowed for a potential integrity violation, but
only if a rather complicated sequence of events occured.
The smallest counterexample requires calling a function {\tt f},
which writes into an uninitialized location $l$ (which is always fine), and then
calls a further function {\tt g} (which should have the effect of sealing $l$
for integrity purposes). Then {\tt g} attempts to write to $l$;
this is allowed because the enforcement mechanism still has
$l$ tagged as $\tagNoDepth$, but violates the integrity property on {\tt f}'s data.
\section{Stack Safety for Lazy Enforcement}
\label{sec:lazy}

@@

First, they eliminate the initialization pass. In this {\em Lazy Tagging}
system, the stack is initially tagged as ``clear.''
\rb{The previous section already presents ``unused'' as the default tag,
though it doesn't say that it can be overwritten whenever}
A function is permitted
to overwrite clear memory, and when it does so its depth tag overwrites
the clear tag, claiming the memory; the remainder of the policy functions
as {\em Depth Isolation}. On return, the callee must clear its frame, which
is still a heavy cost.

To eliminate this cost, \citet{DBLP:conf/sp/RoesslerD18} introduce
{\em Lazy Tagging and Lazy Clearing}. Under this optimizations,
the policy does not initialize stack frames on entry or clear them on exit,
and it permits all writes to the stack, even when the $\PCname$ tag
does not match the memory tag. Instead it propagates the \(\PCname\) tag
to written memory. Then reads from the stack do still require $\PCname$
tag and memory tag to match. Thus, even if a callee illicitly writes to
a private location in its caller, the caller will eventually detect this
if it ever tries to read from that location.
\rb{This is in line with the level of detail in the last section.}
%
These \emph{lazy policies} admit more efficient implementations, but
they deliberately allow violations of stack integrity temporarily,
with the checks deferred until the point a violation truly becomes
harmful. The natural question then is, how do we characterize the
protections provided by these policies once stack safety is broken?
How does a harmful violation that must be caught later differ from a
harmless one?

@@

We first notice that, in principle, these properties appear to enforce
confidentiality outright. So we wish in particular to find an integrity
property. The intuition is that sealed memory can change, but it is
then tainted, and its original owner cannot actually read it. This
leads us to a hybrid of integrity and confidentiality.

For simplicity, our definitions return to the simple stack without sharing,
but all properties in this section can be extended to more complex settings
very naturally.

\definition
For any \(\MPCT,\brk \in \MPCT^*\), let \(\head(\MPCT) = \mach,\pol,\context\) and
suppose that \(\last(\MPCT) = \mach',\pol',\context'\) and
\((\mach',\pol',\context') \hookrightarrow \MPCT'\). Find the set of components
that changed during the call, \(\components = \prot(\context) \cap \Delta(\mach,\mach')\).
A system enjoys {\em deferred stepwise integrity} if for any \(\nach\) such that
\(\mach' \approx_{\components'} \nach\) and its induced trace
\((\nach,\pol',\context') \hookrightarrow \NPCT\), \(\MPCT' \doteq \NPCT\).

In short, if sealed components are modified during the call, the caller may not
access their values.
%
For example, consider again the integrity violation in
Figure~\ref{fig:int1}. Under a deferred discipline, the write to {\tt
  x} in instruction 11 taints the variable but does not in itself
constitute a violation, which happens only when the tainted value is
read in instruction 4. However, if this instruction added the constant
that was originally stored in {\tt x} without reading the variable,
i.e., {\tt add \$42,\%ra}, deferred integrity would not be violated.
Instead of forbidding such dangerous writes, we say,
``No reads after dangerous writes.''

@@

We argue that while deferred stepwise integrity meaningfully captures the intuition
behind lazy tagging, it stops short of the kind of extensional characterization
that would be viable as a weakest reasonable definition. Consider a hypothetical
taint-tracking policy, that allows dangerous writes to be copied as long as the
taint remains hidden from outside observers. In order to characterize
such a policy, we would need a model of observation.
Similarly, for such a taint-based policy, lockstep confidentiality would be too
strong, as we might permit secrets to move about as long as they were not
leaked to the outside world.

@@

We say that a pair of observation traces $\obsT_1$ and $\obsT_2$ are {\em similar}
as far as an external observer is concerned, written \(\obsT_1 \eqsim
\obsT_2\), if the sequence of non-silent observations is the same. That is, we
compare up to deletion of \(\tau\) observations, coinductively:

@@

\definition
For any \(\MPCT,\brk \in \MPCT^*\),
let \(\head(\MPCT) = \mach,\pol,\context\).
%
Then, supposing that \(\last(\MPCT) = \mach',\pol',\context'\),
let \(\components\) be the set of protected components that changed during
the call, \(\components = \prot(\context) \cap \Delta(\mach, \mach')\),
and let \((\mach,\pol',\context') \hookrightarrow \MPCT'\).
A system enjoys {\em observational integrity} if for any \(\nach\) such that
\(\mach' \approx_{\components'} \nach\), and its induced trace
\((\nach,\pol',\context') \hookrightarrow \NPCT\), \(\obsof(\MPCT') \simeq \obsof(\NPCT)\).

@@

\definition
For any \(\MPCT,\brk \in \MPCT^*\),
let \(\head(\MPCT) = \mach,\pol,\context\) and
\(\components = \secret(\context)\).
%
A system enjoys {\em observational confidentiality} if for all
\(\nach\) such that \(\mach \approx_\components \nach\) and
\(\nach \hookrightarrow \NPCT | \brk(\MPCT)\),
\(\MPCT\) and \(\NPCT\), the following conditions all hold:

\begin{itemize}
\item They are observationally equivalent, \(\obsof(\MPCT) = \obsof(\NPCT)\),
  meaning that no secrets leak during the call
\item \(\brk ~ \last(\MPCT) \leftrightarrow \brk ~
\last(\NPCT)\)---if one call returns, so does the other
\item Assuming both calls return, let \(\last(\MPCT) = \mach',\pol',\context'\)
  and \(\pi_\mach(\last(\NPCT)) = \nach'\).
  Let \(\components' = \components \cap \bar{\Diamond}(\mach,\mach',\nach,\nach')\).
  And let \(\nach''\) be a state such that \(\mach' \approx_\components \nach''\).
  Then if \(\mach',\pol',\context' \hookrightarrow \MPCT'\) and
  \(\nach',\pol',\context' \hookrightarrow \NPCT'\), it must be
  that \(\obsof(\MPCT') \simeq \obsof(\NPCT')\)
\end{itemize}

@@

Observable properties allow us to defer enforcement until a property
violation would become visible, as in lazy policies. But by formalizing
the connection to the eager policy, we can identify when lazy policies
miss violations that can become visible. The {\em Lazy Tagging and Clearing}
micro-policy from \citet{DBLP:conf/sp/RoesslerD18} tags each stack slot with the call depth
at which it was written, and enforces that it must be read from the
same depth. However, this allows violations of observable stack safety!
Specifically, a callee might write into the stack and leave tags behind
for a future callee at the same depth to read. This violates confidentiality and,
if the writes were in the caller's frame, integrity.

{\em Lazy Tagging and Clearing} can be repaired if, instead of tagging each function
activation with its depth in the stack, we generate a fresh activation
identifier on each call, which prevents a program from exploiting stale
tags from previous activations. A related mechanism was explored in the
Static Authorities policy of \citet{DBLP:conf/sp/RoesslerD18}, which
associates a unique activation identifier to each function, which is
however shared by all activations of the same function in order to obtain
good cacheability of tag rules, but that policy allows leaks between
instances of the same function.

@@

\vspace*{-1ex}
\judgmentthree[ReturnRec]
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
              {\(\domMap'' = \mathit{pop} ~ \domMap' ~ |\rts|\)}
              {\(\mach,(\domMap,\underscore::\rts) \stepsto_C \domMap'',\rts'\)}

\vspace*{-3.5ex}
\judgment[ Default]
         {}
         {\(\underscore,\context \stepsto_C \context\)}

\definition Let the protected set of a context, \(\prot_P(\domMap,\rts)\),
be the set of components \(\component\) such that either \(\domMap ~ \component = \sealed{\underscore}\)
or \(\domMap ~ \component = \passed{\depth,\depth'}\) and \(|\rts| < \depth\) or
\(|\rts| > \depth'\).

\definition
For each of the stepwise, deferred, and observational versions of
stack integrity in the simple model, the equivalent property in the
passing model substitutes the above definitions of \(\context\), initial contexts and update
function, and \(\prot_P\) for their simple equivalents, and is otherwise identical.

\definition Let the secret set of a context, \(\secret_P(\domMap,\rts)\),
be the set of components \(\component\) such that
\(\domMap ~ \component = \sealed{\underscore}\) or
\(\domMap ~ \component = \passed{\depth,\depth'}\)
where \(\depth \leq |\rts| \leq \depth'\).

\definition
For both the stepwise and observational versions of stack confidentiality in
the original model, the equivalent property in the passing model is the same after
substituting the above definitions of \(\context\), initial contexts and update
function, and \(\prot_P\) for their simple equivalents.

@@

Stack integrity and confidentiality apply in the coroutine model, based on straightforward
projections of each stack's domains, etc. and the machinery of the passing model. We will give
the coroutine-specific properties.

%\definition
%The protected and secret sets of a context as used for calls,
%\(\prot_C(\domMap,\rtm,\yts,\stackid)\) and \(\secret_C(\domMap,\rtm,\yts,\stackid)\),
%are equivalent to their counterparts \(\prot_P\) and \(\secret_P\) applied to a domain map
%that projects out the stack domains of components in stack \(\stackid\) and a
%return target stack \(\rts = \rtm ~ \stackid\). Intuitively, within the active stack we protect
%the same components we would have in the passing model.

%\definition
%For each of the stepwise, deferred, and observational versions of
%stack integrity in the simple model, the equivalent property in the
%passing model substitutes the above definitions of \(\context\), initial contexts and update
%function, and \(\prot_C\) for their simple equivalents, and is otherwise identical.

%\definition \(\MPCT^*\) is now defined as
%\[\begin{aligned}
%\bigcup_{\stackid \in \STACKS,\depth \in \mathbb{Z}} \hspace{-1em} \{\MPCT | \MPCT\langle f_\depth \rangle
%\text{ is a reachable segment}\} \hspace{1em} &
%\text{where } f_\depth ~ (\mach,\pol,(\domMap,\rtm,\yts,\stackid')) \triangleq |\rtm ~ \stackid| \geq \depth \\
%\end{aligned}\]
%and \(\brk{\MPCT}\) similarly projects the depth of the active stack.

%\definition
%For either of the stepwise and observational versions of
%stack confidentiality in the passing model, the equivalent property in the
%coroutine model substitutes the above definitions.

\definition \(\MPCT^\wedge\) is the \emph{yield set}, defined as
\[\begin{aligned}
\bigcup_{\stackid \in \STACKS} \hspace{-.5em} \{\MPCT, \neg f_\stackid | \MPCT\langle f_\stackid \rangle
\text{ is a reachable segment}\} \hspace{1em} &
\text{where } f_\stackid ~ (\underscore,\underscore,(\underscore,\underscore,\underscore,\stackid')) \triangleq \stackid \not = \stackid' \\
\end{aligned}\]

Here, we are capturing the entire span that the system spends {\em away} from a given
coroutine.

\definition
Let the protected set of a context, \(\prot_Y(\domMap,\rtm,\yts,\stackid)\),
be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid'}{\underscore}\) where \(\stackid \not = \stackid`\).

\definition
Let the secret set of a context, \(\secret_Y(\domMap,\rtm,\yts,\stackid)\),
be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid'}{\underscore}\) where \(\stackid \not = \stackid`\).

>>>>

\vspace*{-1ex}
\judgmentthree[ReturnRec]
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
              {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
              {\(\domMap'' = \domMap'[\components \mapsto \unsealed]\)}
              {\(\mach,(\domMap,\_::\rts) \stepsto_C \domMap'',\rts'\)}

\vspace*{-3.5ex}
\judgment[ Default]
         {}
         {\(\_,\context \stepsto_C \context\)}

@@

\definition
Let the protected set of a context, \(\mathit{protected}(\domMap,\rts)\), be the
set of components \(\component\) such that \(\domMap ~ \component = \sealed{\depth}\)
for some depth \(\depth\).

\definition
A system enjoys \textit{\textbf{stepwise stack integrity}} if, for any reachable state
\(\mpcstatename\) such that \(\mpcstatename \stepstocon \mpcstatename'\),
and any component \(\component \in \mathit{protected}(\domMap,\rts)\),
\(\pi_\mach(\mpcstatename') ~ \component = \pi_\mach(\mpcstatename) ~ \component\).
\apt{but now $dm$ and $rts$ are unbound}.

@@

\definition \(\MPCT^*\) is the set of all \emph{call traces}, defined as
\[\begin{aligned}
\bigcup_{\depth \in \mathbb{Z}} \{\MPCT | \MPCT\langle f_\depth \rangle
\text{ is a reachable segment}\} \hspace{1em} &
\text{where } f_\depth ~ (\mach,\pol,(\domMap,\rts)) \triangleq |\rts| \geq \depth \\
\end{aligned}\]

\definition
For each trace \(\MPCT \in \MPCT^*\) with \(\head(\MPCT) = \_,\_,(\_,\rts)\), the
{\em break condition} of \(\MPCT\) is a predicate on
states defined as \(\mathit{brk}(\MPCT) = \neg f_{|\rts|}(\MPCT)\). It follows from our definitions
that this holds on \(\MPCT\)'s final state, {\em unless it terminated prematurely due to a failstop}.

@@

\begin{minipage}{.3\textwidth}
\judgment{}
         {\(\mpcstatename \doteq \npcstatename\)}
\end{minipage}
\begin{minipage}{.6\textwidth}
\judgmenttwo{\(\mach, \pi_\mach(\head(\machT)) \diamond \nach, \pi_\mach(\head(\nachT))\)}
            {\(\machT \doteq \nachT\)}
            {\(\notfinished{(\mach,\_,\_)}{\machT} \doteq \notfinished{(\nach,\_,\_)}{\nachT}\)}
\end{minipage}

\definition
Let the secret set of a context, \(\mathit{secret}(\domMap,\rts)\), be the
set of components \(\component\) such that \(\domMap ~ \component \not = \outside\).

\definition
For any call trace \(\MPCT \in \MPCT^*\) with \(\head(\MPCT) = \mach,\pol,\context\),
let \(\components = \mathit{secret}(\context)\) and \(\nach\) be any variant
such that \(\mach \approx_\components \nach\).
A system enjoys \textbf{\textit{stepwise stack confidentiality}} if,
for all \(\NPCT\) such that \(\nach,\pol,\domMap \hookrightarrow \NPCT | \mathit{brk}(\MPCT)\),
\(\MPCT \doteq \NPCT\) holds.\apt{I'm worried about quantifier order here. Surely $n$ needs to be
universally quantified, and probably also \(\MPCT\) (?) }

@@

In other words, stepwise stack confidentiality states that if, at the start of the call,
we vary all stack locations that are supposed to be secret from the callee
(which in our simple setting is the entirety of the stack),
the resulting trace remains in lockstep with the original trace
until either both return together or one failstops. This implies that
if the callee reads a secret location, it must failstop.\apt{right?}
%
Note that \(\MPCT\) may contain nested calls; these must also respect the secrecy
of the components in \(\components\), and in addition their subtraces are also in
\(\MPCT^*\), and therefore confidentiality must hold on them separately. \(\NPCT\)
will contain these calls and returns as well, so its return stack pushes and pops
in lockstep until it breaks at the final return.

Finally, we formalize a version of WBCF, which captures the same informal idea
as that of \citet{Skorstengaard+19b} using our context machinery.
\definition
A system enjoys \textit{\textbf{well-bracketed control flow}} when, for every pair of reachable states
\(\mpcstatename = (\_,\_,(\_,\rts))\) and
\(\mpcstatename' = (\_,\_,(\_,\rts'))\) such that
\(\mpcstatename \stepsto \mpcstatename'\)\apt{doesn't reachability of $\mpcstatename$ imply reachability of $\mpcstatename'$?}, if \(|\rts'| < |\rts|\), then
\(|\rts'| = |\rts|\)

@@

%\definition A system enjoys {\em well-bracketed control flow} if for all
%reachable states \(\mpcstatename\) and \(\mpcstatename'\) such that
%\(\mpcstatename \stepstocon \mpcstatename'\), if
%\(\pi_c(\mpcstatename) = (\_, \_::\rts)\) and \(\pi_m(\mpcstatename)\)
%is annotated as a return, then \(\pi_c(\mpcstatename) = (\_, \rts)\).

@@

%\definition A system enjoys {\em well-structured control flow} if for all
%reachable states \(\mpcstatename\) and \(\mpcstatename'\) such that
%\(\mpcstatename \stepstocon \mpcstatename'\), if
%\(\pi_c(\mpcstatename) = (\_,\_,\_,\stackid)\) and \(\pi_m(\mpcstatename)\)
%is annotated as a return, then \(\pi_c(\mpcstatename) = (\_,\_,\_,\stackid')\)
%where \(\stackid \not = \stackid'\).

@@

Naturally, testing also revealed a number of errors in our
implementation of the enforcement mechanism (the original was written in C++
and targeted ARM machine code
%\bcp{right?}\leo{yeah}
; we re-implemented it in Coq targeting RISC-V).  These errors ranged
from trivial typos to ones that required an intriguingly complex setup
to appear.  The most interesting bug (included in the table as row
{\em HEADER\_NO\_INIT}) was that, on our first try, the blessed call
sequence %/policy combination\apt{??}
did not initialize all locations for the
newly allocated stack frame correctly, but left some of them as
$\tagNoDepth$. This allowed for a potential integrity violation, but
only if a rather complicated sequence of events occured.
The smallest counterexample requires calling a function {\tt f},
which writes into an uninitialized location $l$ (which is always fine\apt{is it??? in the strict policy?}, and then
calls a further function {\tt g} (which should have the effect of sealing $l$
for integrity purposes). Then {\tt g} attempts to write to $l$;
this is allowed because the enforcement mechanism still has
$l$ tagged as $\tagNoDepth$, but violates the integrity property on {\tt f}'s data.
\section{Stack Safety for Lazy Enforcement}
\label{sec:lazy}

@@

First, they eliminate the initialization pass. In this {\em Lazy Tagging}
system, the stack is initially tagged as ``clear.''
\rb{The previous section already presents ``unused'' as the default tag,
  though it doesn't say that it can be overwritten whenever\apt{but see my
query re the HEADER\_NO\_INIT bug}}
A function is permitted
to overwrite clear memory, and when it does so its depth tag overwrites
the clear tag, claiming the memory; the remainder of the policy functions
as {\em Depth Isolation}. On return, the callee must clear its frame, which
is still a heavy cost.

To eliminate this cost, \citet{DBLP:conf/sp/RoesslerD18} augment Lazy Tagging
with {\em Lazy Clearing}. Under this combination of optimizations,
the policy does not initialize stack frames on entry \emph{or} clear them on exit,
and it permits all writes to the stack, even when the $\PCname$ tag
does not match the memory tag; the \(\PCname\) tag is always propagated
to the written location. Reads from the stack do still require $\PCname$
tag and memory tag to match. Thus, even if a callee illicitly writes to
a private location in its caller, the caller will eventually detect this
if it ever tries to read from that location.
\rb{This is in line with the level of detail in the last section.}
%
These \emph{lazy policies} admit more efficient implementations, but
they deliberately allow temporary violations of stack integrity,
with the checks deferred until the point a violation truly becomes
harmful. The natural question then is: how do we characterize the
protections provided by these policies once stepwise stack safety is broken?
How does a harmful violation that must be caught later differ from a
harmless one?

@@

We first notice that, in principle\apt{??}, these properties appear to enforce
confidentiality outright. So we wish in particular to find an integrity
property. The intuition is that sealed memory can change, but it is
then tainted, and its original owner cannot actually read it. This
leads us to a hybrid of integrity and confidentiality.

%For simplicity, our definitions return to the simple stack without sharing,
%but all properties in this section can be extended to more complex settings
%very naturally.

\definition
For any \(\MPCT \in \MPCT^*\), let \(\head(\MPCT) = \mach,\pol,\context\) and
suppose that \(\last(\MPCT) = \mach',\pol',\context'\) and
\((\mach',\pol',\context') \hookrightarrow \MPCT'\). Let 
\(\components = \mathit{protected}(\context) \cap \Delta(\mach,\mach')\), the
set of sealed components that changed during the call.
A system enjoys \textbf{\textit{deferred stepwise integrity}} if, for any \(\nach'\) and \(\NPCT'\)
such that \(\mach' \approx_{\components} \nach'\) and 
\((\nach',\pol',\context') \hookrightarrow \NPCT'\), \(\MPCT' \doteq \NPCT'\) holds.\apt{again, shouldn't
we quantify over all $M$?}

In short, if sealed components are modified during the call, the caller may not
access their values.\apt{This is pretty cryptic.}
%
For example, consider again the integrity violation in
Figure~\ref{fig:int1}. Under a deferred discipline, the write to {\tt
  x} in instruction 11 taints the variable but does not in itself
constitute a violation, which happens only when the tainted value is
read in instruction 4. However, if this instruction added the constant
that was originally stored in {\tt x} without reading the variable,
i.e., {\tt add \$42,\%ra}, deferred integrity would not be violated.
Instead of strictly forbidding such dangerous writes, we say,
``No reads after dangerous writes.''

@@

\apt{Given that the deferred property suffices to specifcy the lazy policies,
  the case for observable properties is pretty weak.  Should we just cut them?}

We argue that while deferred stepwise integrity meaningfully captures the intuition
behind lazy tagging, it stops short of the kind of extensional characterization
that would be viable as a weakest reasonable definition. Consider a hypothetical
taint-tracking policy that allows dangerous writes to be copied as long as the
taint remains hidden from outside observers. In order to characterize
such a policy, we would need a model of observation.
Similarly, for such a taint-based policy, lockstep confidentiality would be too
strong, as we might permit secrets to move about as long as they were not
leaked to the outside world.

@@

We say that two observation traces $\obsT_1$ and $\obsT_2$ are {\em similar}
as far as an external observer is concerned, written \(\obsT_1 \eqsim
\obsT_2\), if the sequence of non-silent observations is the same. That is, we
compare up to deletion of \(\tau\) observations, coinductively:

@@

\definition
For any call trace \(\MPCT \in \MPCT^*\),
let \(\head(\MPCT) = \mach,\pol,\context\).
%
Then, supposing that \(\last(\MPCT) = \mach',\pol',\context'\),
let \(\components\) be the set of protected components that changed during
the call, \(\components = \mathit{protected}(\context) \cap \Delta(\mach, \mach')\),
and let \((\mach,\pol',\context') \hookrightarrow \MPCT'\).
A system enjoys {\em observational integrity} if for any \(\nach\) such that
\(\mach' \approx_{\components'} \nach\), and its induced trace
\((\nach,\pol',\context') \hookrightarrow \NPCT\), \(\obsof(\MPCT') \simeq \obsof(\NPCT)\).
\apt{Adjust quantification to match final version of deferred intergrity.}

@@

\definition
For any call trace \(\MPCT \in \MPCT^*\),
let \(\head(\MPCT) = \mach,\pol,\context\) and
\(\components = \mathit{secret}(\context)\).
%
A system enjoys {\em observational confidentiality} if for all
\(\nach\) such that \(\mach \approx_\components \nach\) and
\(\nach \hookrightarrow \NPCT | \mathit{brk}(\MPCT)\),
\(\MPCT\) and \(\NPCT\), the following conditions all hold:

\begin{itemize}
\item They are observationally equivalent, \(\obsof(\MPCT) = \obsof(\NPCT)\),
  meaning that no secrets leak during the call
\item \(\mathit{brk}(\MPCT) ~ \last(\MPCT) \leftrightarrow \mathit{brk}(\MPCT) ~
\last(\NPCT)\)---if one call returns, so does the other
\item Assuming both calls return, let \(\last(\MPCT) = \mach',\pol',\context'\)
  and \(\pi_\mach(\last(\NPCT)) = \nach'\).
  Let \(\components' = \components \cap \bar{\Diamond}(\mach,\mach',\nach,\nach')\).
  And let \(\nach''\) be a state such that \(\mach' \approx_\components \nach''\).
  Then if \(\mach',\pol',\context' \hookrightarrow \MPCT'\) and
  \(\nach',\pol',\context' \hookrightarrow \NPCT'\), it must be
  that \(\obsof(\MPCT') \simeq \obsof(\NPCT')\)\apt{adjust quantification if needed}
\end{itemize}

@@

Observable properties allow us to defer enforcement until a property
violation would become visible, as in lazy policies. But by formalizing
the connection to the eager policy\apt{???}, we can identify when lazy policies
miss violations that can become visible. The {\em Lazy Tagging and Clearing}
micro-policy from \citet{DBLP:conf/sp/RoesslerD18} tags each stack slot with the call depth
at which it was written, and enforces that it must be read from the
same depth. However, this allows violations of observable stack safety!
Specifically, a callee might write into the stack and leave tags behind
for a future callee at the same depth to read. This violates confidentiality and,
if the writes were in the caller's frame, integrity.

{\em Lazy Tagging and Clearing} can be repaired if, instead of tagging each function
activation with its depth in the stack, we generate a fresh activation
identifier on each call, which prevents a program from exploiting stale
tags from previous activations. A related mechanism was explored in the
Static Authorities policy of \citet{DBLP:conf/sp/RoesslerD18}, which
associates a unique activation identifier to each function, which is
however shared by all activations of the same function in order to obtain
good cacheability of tag rules---but that policy allows leaks between
instances of the same function.

@@

\vspace*{-1ex}
\judgmentthree[ReturnRec]
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
              {\(\domMap'' = \mathit{pop} ~ \domMap' ~ |\rts|\)}
              {\(\mach,(\domMap,\_::\rts) \stepsto_C \domMap'',\rts'\)}

\vspace*{-3.5ex}
\judgment[ Default]
         {}
         {\(\_,\context \stepsto_C \context\)}

\definition Let the protected set of a context, \(\mathit{protected}_P(\domMap,\rts)\),
be the set of components \(\component\) such that either \(\domMap ~ \component = \sealed{\_}\)
or \(\domMap ~ \component = \passed{\depth,\depth'}\) and \(|\rts| < \depth\) or
\(|\rts| > \depth'\).

\definition
For each of the stepwise, deferred, and observational versions of
stack integrity in the simple model, the equivalent property in the
passing model substitutes the above definitions of \(\context\), initial contexts and update
function, and \(\mathit{protected}_P\) for their simple equivalents, and is otherwise identical.

\definition
For any call trace \(\MPCT \in \MPCT^*\) with \(\head(\MPCT) = \mach,\pol,(\domMap,\rts)\),
let \(\components\) be the set of components \(\component\) such that
\(\domMap ~ \component = \outside\) or \(\domMap ~ \component = \passed{\depth,\depth'}\)
and \(\depth \leq |\rts| \leq \depth'\). A system enjoys
\emph{stepwise stack confidentiality} if,
for all \(\nach\) such that \(\mach \approx_\components \nach\) and
\(\nach \hookrightarrow \NPCT | \neg f_{|\rts|}\),
\(\MPCT \doteq \NPCT\).

@@

\definition Let the call-protected set of a context,
\(\mathit{protected}_C(\domMap,\rtm,\yts,\stackid)\),
be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid}{\sealed{\_}}\)
or \(\domMap ~ \component = \instack{\stackid}{\passed{\depth,\depth'}}\) and \(|\rtm ~ \stackid| < \depth\) or
\(|\rtm ~ \stackid| > \depth'\).

\definition
For each of the stepwise, deferred, and observational versions of
stack integrity in the simple model, the equivalent property in the
passing model substitutes the above definitions of \(\context\), initial contexts and update
function, and \(\mathit{protected}_C\) for their simple equivalents, and is otherwise identical.

\definition Let the yield-protected set of a context,
\(\mathit{protected}_Y(\domMap,\rtm,\yts,\stackid)\),
be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid'}{\_}\) where \(\stackid \not = \stackid`\).

\definition
We define {\em stepwise coroutine integrity} in the same way as stepwise stack integrity,
substituting the above definitions of \(\context\), initial contexts and update
function, and \(\mathit{protected}_Y\) for their equivalents. Likewise
{\em deferred coroutine integrity} and {\em observational coroutine integrity} are defined
in terms of their simple equivalents.

\definition Let \(\stackid\) be a stack identifier, \(\depth\) be any depth, and
\(f_\depth ~ \mach ~ (\_, \rtm, \_, \stackid)\) hold for \(|\rtm ~ \stackid| \geq \depth\).
For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\rtm,\yts,\stackid)\). Let
\(\components\) be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid}{\unsealed}\) or
\(\instack{\stackid}{\passed{\depth,\depth'}}\)
where \(\depth \leq |\rtm ~ \stackid| \leq \depth'\) .
Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
\(\nach \hookrightarrow \NPCT\langle f_\depth \rangle\). A system enjoys
{\em stepwise stack confidentiality} in the coroutine setting if for all
such \(\MPCT\) and \(\NPCT\), \(\MPCT \doteq \NPCT\).
